Fusion Moves for Correlation Clustering

### 2014-11-07 paper/egpaper_for_review.tex
added real numbers to hc fig

But EHC is very fast, and can be used to initialize
CGC \cite{beier_2014_cvpr}. Plenty of the time in CGC
is spend in the \emph{cut phase} to solve the 
first 2 coloring on the complete graph.

Therefore we propose to initialize  CGC with EBHC
and hope to speedup of CGC with this starting point.

%Furthermore, we propose a algorithm to combine / fuse together
%multiple EBHC results from perpetuated energies.
%This algorithm, namely 
%Correlation-Clustering-Fusion (CCF) Moves 
%will be discussed in the following section.

>>>>

But EHC is very fast, and can be used to initialize
CGC \cite{beier_2014_cvpr}. Excessive time in CGC
is spend in the \emph{cut phase} to solve the 
first 2 coloring on the complete graph.
As shown in ~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.
